Country-Level Impact of Education on Entrepreneurship

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

Of course, what determines entrepreneurship at a country-level has been long searched already but although economic, demographic or geographic factors have been looked at extensively, much less has been done regarding cultural or educational factors. Yet, “the relative stability of differences in entrepreneurship across countries suggests that factors other than economic ones are at play” [@Freytag2007] ?????? 2010 VERSION MAIN BIB ?????. Even if “in recent years research has increasingly devoted itself to the subject” [@OECD2009], a lot still needs to be done.

@@

Besides potential educational effects on self-confidence and social capital, we will need to control for all classic entrepreneurship determinants. Therefore, we will quote Grilo and Thurik’s research [@Grilo2005b] about what determines entrepreneurship engagement levels throughout the European Union and the US, Wennekers, Ulhaner and Thurik’s about variation across countries [@Wennekers2002], Freytag and Thurik about determinants in a cross-country setting ????? 2010 VERSION MAINBIB ?????.

>>>>

Grilo and Thurik’s research [@Grilo2005b] is also often refered to about what determines entrepreneurship engagement levels throughout the European Union and the US.

Wennekers, Ulhaner and Thurik have looked more into variation across countries [@Wennekers2002]

Also focused on environmental factors, Freytag and Thurik have studied determinants in a cross-country setting ????? 2010 VERSION MAINBIB ?????.

Thus, what determines entrepreneurship at a country-level has been long searched already but although structural factors have been looked at extensively, much less has been done regarding cultural or educational factors. Yet, “the relative stability of differences in entrepreneurship across countries suggests that factors other than economic ones are at play” [@Freytag2007] ?????? 2010 VERSION MAIN BIB ?????. Even if “in recent years research has increasingly devoted itself to the subject” [@OECD2009], a lot still needs to be done.

@@
